### 2023-12-05 doc/Thesis/chapter/04-experimental.tex
correction transfer until excl 5.2 EMMA

\iffalse
\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
		\label{fig:sol-aq}
		\caption{Aquatic solution}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
		\label{fig:sol-bu}
		\caption{Buthanolic solution}
	\end{subfigure}
	\label{fig:sol}
	\caption{Aquatic and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
\end{figure}
\iffalse

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization}
\td{All \gls{sem} micrographs were taken with a Zeiss Supra 40. (conditions? were samples sputtered etc...)}
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
\end{figure}

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
\SI{10}{\milli\volt}.
Prior to \gls{iv} measurements the samples were sputtered with aluminium 
through a mask to produce a multitude of equidistant contacts with a Leybold 
UNIVEX450C Sputter System.
Directional current sputtering was used with Argon as inert gas at \SI{0.005}{\milli\bar} 
and with a power of \SI{40}{\watt} for \SI{700}{\second}.
Between sputtering and \gls{iv} measurements 
direct contacts to the steel substrate were created by removing a patch of the \gls{zro}
layer with 
sand paper on two opposing edges of a sample and then by applying silver paste.
See figure~\ref{fig:circuit} for a sketch of the connectivity.

@@

@@

(i.e. my brain) in order to obtain reasonable constraints for computerized pre-optimization. 

@@

Composition of the aquatic solution, heating program, blade distance (distance between 

@@

After the blade moved over the substrate the remaining liquid needed about a minute 
to evaporate at room temperature. 

@@

relative concentration of Zr $c_{zr}$, number of layers $\lambda$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively. 

@@

	\caption{Pre-optimization experiments}

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed comparable passivization results and better stability of the solution. 
Therefore \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

>>>>

\iffalse
\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
		\label{fig:sol-aq}
		\caption{Aquatic solution}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
		\label{fig:sol-bu}
		\caption{Buthanolic solution}
	\end{subfigure}
	\label{fig:sol}
	\caption{Aquatic and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
\end{figure}
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization}
\td{All \gls{sem} micrographs were taken with a Zeiss Supra 40. (conditions? were samples sputtered etc...)}
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
in Opus software. % included in the spectrometer. 
\td{\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. (where are the conditions?)}
All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.\td{(what is XXX circuit?)}}
\end{figure}

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
\SI{10}{\milli\volt}.
Prior to \gls{iv} measurements the samples were sputtered with aluminium 
through a mask to produce a multitude of equidistant contacts with a Leybold 
UNIVEX450C Sputter System.
Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} 
and with a power of \SI{40}{\watt} for \SI{700}{\second}.
Between sputtering and \gls{iv} measurements 
direct contacts to the steel substrate were created by removing a patch of the \gls{zro}
layer with 
sand paper on two opposing edges of a sample and then by applying silver paste.
See figure~\ref{fig:circuit} for a sketch of the connectivity.

@@

\td{preopt of what? recipe?}

@@

(i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 

@@

Composition of the \td{aquatic solution (I thought this did not work?)}, heating program, blade distance (distance between 

@@

\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}

@@

relative concentration of Zr $c_{zr}$, \td{number of layers $\lambda$ (layers of what?)}, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively.

@@

	\caption{Pre-optimization experiments \td{(still smaller?? why? what am I supposed to learn?)} }

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilization agent was changed from \todo{ \gls{acoh} to \gls{ipo} (but why?)} because of much better \td{solution stability. (how did yo test this??)}
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed \td{comparable passivization results (but where are they?)} and better stability of the solution. 
Therefore \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

### 2023-12-05 doc/Thesis/chapter/061-results-emma.tex
correction transfer until excl 5.2 EMMA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) have been investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The sample predicted as best by the algorithm is experiment number 13 with 
lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) was investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The \td{best (what is "best"? How do you measure that?	 recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The sample predicted as best by the algorithm is experiment number 13 with 
lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.
